\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-30 syntax.tex
comments

$$
\Rule[name=Ept Sig]
{}
{\goodSig{\Gamma}{\nu\cdot}{0}}
\quad
\Rule[name=Sig Add]
{\goodSig{\Gamma}{\sigma}{n} 
 \quad \goodSeal{\Gamma}{f}{\sigma}{A}\YZ{How should I understand 'f' and 'A'?}\EDJreply{`f' is the seal, 'A' is the result of sealing. I think I wrote down the motivation of sealing... Is it still too hard? Do you think I need to think of a more friendly way?}\YZreply{Yes, still too rough on the reader. I sense that this part is central to the metatheory, so it is worth explaining the details well.}
 \quad \goodType{\Gamma, A}{T}{i}}
{\goodSig{\Gamma}{(\nu^+ \ \sigma \ \{f\} \ T)}{n+1}}
$$

@@

The reason we need this additional type construct of $\cC\sigma$ here is
to support \textit{code reuse}, as the rule of linkages hinders its
ability to do abstraction. Concretely speaking, (using surface syntax)
we don't have \\ $\goodTerm{\Gamma, \cL(\{a~:~\bW \sigma; b~:~a \to
T\})}{h}{\cL(\{a~:~\cU; b~:~a \to T\})}$\footnote{If we had one,
consider the case $T$ is bottom type and $\sigma$ is empty record and
thus $a$ is initially bottom type. Now the direct projection using \ruleref{Sig Proj} $\goodTerm{\Gamma, a : \cU}{h.b}{a \to \bot}$ will lead to problem because every field in linkage has this implicit universal quantification, and for this case we can substitute $a$ with arbitrary type, say $\top$: $\goodTerm{\Gamma}{h.b[a \mapsto \top]}{\top \to \bot}$ is a contradiction\YZ{You are talking about
overriding here, but you haven't told the reader what overriding means
in your metatheory.}\EDJreply{Ok. I use the projection now instead.}}. This term is important for us to abstract the
concrete inductive type so that the later field can depend on the
abstract interface and achieve \textit{code reuse}. On the other hand,
we do have $\goodTerm{\Gamma, (\Sigma a : \bW\sigma, a \to T)
}{h}{(\Sigma a : \cU, a \to T)}$ because of the rule for existential
(also existential type just don't allow overriding\YZ{Why is it desired that this type in the context does not allow overriding (since it already says 'a : U')?}).
Thus to allow abstraction happens, we need $\cC\sigma$ to compile a
linkage to module as a part of the context and we also need
\ruleref{Lnkg Compile} to specify the compilation from linkage to
module.

@@

Sealing judgement is still about the important term $h$ we mentioned
earlier. Thanks to $\cC$, a newly added field $t_{new}$ after $a$ \YZ{By 'a newly
added term', do you mean a term that follows field 'a'?}\EDJreply{Thanks. Fixed} is now in the
context containing $\cC\{a : \bW \sigma; ..\}$.
But if we want $t_{new}$ to be inherited(reused) when $\sigma$ is
extended, we would like $t_{new}$ to be in the context containing
$\cC\{a : \cU; ..\}$ instead. The sealing is responsible for this
because we have a sealing $\goodTerm{\Gamma, \cC\{a : \bW \sigma;
..\}}{s}{\cC\{a : \cU; ..\}}$ = $\goodTerm{\Gamma, (\Sigma a : \bW
\sigma,..)}{s}{(\Sigma a : \cU,..)}$. Then we can construct
$t_{new}$ in the context containing $(\Sigma a : \cU,..)$, ready for
inheritance.
Apparently $t_{new}$ in this case cannot be doing \textit{exhaustiveness
checking}, but it can freely use any \textit{exhaustiveness-checked}
recursor.
%\YZ{It occurs to me that you use the word "sealing" to mean
%different (though tangentially related) things. Previously you used it
%as in "sealed families".}\EDJreply{They are actually the same thing.
%This sealing in metatheory is much stronger than that of the implemented
%plugin. Downside of the strong sealing is that if the user really use
%this version of sealing, the user will have to annotate what the sealed
%family type is. Now in the plugin, the sealed family type is almost
%fixed (directly inferred using a fixed rules). So basically this
%complete version of sealing (in metatheory) can deduce that of seal (in
%plugin implementation)}

>>>>

$$
\Rule[name=Ept Sig]
{}
{\goodSig{\Gamma}{\nu\cdot}{0}}
\quad
\Rule[name=Sig Add]
{\goodSig{\Gamma}{\sigma}{n} 
 \quad \goodSeal{\Gamma}{f}{\sigma}{A}
 \quad \goodType{\Gamma, A}{T}{i}}
{\goodSig{\Gamma}{(\nu^+ \ \sigma \ \{f\} \ T)}{n+1}}
$$

@@

The reason we need this additional type construct of $\cC\sigma$ here is
to support \textit{code reuse}, as the rule of linkages hinders its
ability to do abstraction. Concretely speaking, (using surface syntax)
we don't have \\ $\goodTerm{\Gamma, \cL(\{a~:~\bW \sigma; b~:~a \to
T\})}{h}{\cL(\{a~:~\cU; b~:~a \to T\})}$\footnote{If we had one,
consider the case $T$ is bottom type and $\sigma$ is empty record and
thus $a$ is initially bottom type. Now the direct projection using
\ruleref{Sig Proj} $\goodTerm{\Gamma, a : \cU}{h.b}{a \to \bot}$ will
lead to problem because every field in linkage has this implicit
universal quantification, and for this case we can substitute $a$ with
arbitrary type, say $\top$: $\goodTerm{\Gamma}{h.b[a \mapsto \top]}{\top
\to \bot}$ is a contradiction}.
This term is important for us to abstract the
concrete inductive type so that the later field can depend on the
abstract interface and achieve \textit{code reuse}.
\YZ{It reads as if you want to have 'h : L\{a : U, b : a -> T\}'. But it is problematic because it leads to inconsistency, as you describe in a footnote.}
On the other hand,
we do have $\goodTerm{\Gamma, (\Sigma a : \bW\sigma, a \to T)
}{h}{(\Sigma a : \cU, a \to T)}$ because of the rule for existential
(also existential type just don't allow overriding\YZ{This sentence still speaks of overriding. Explain in terms of projection instead?}).
Thus to allow abstraction happens, we need $\cC\sigma$ to compile a
linkage to module as a part of the context and we also need
\ruleref{Lnkg Compile} to specify the compilation from linkage to
module.

@@

Sealing judgement is still about the important term $h$ we mentioned
earlier. Thanks to $\cC$, a field $t_{new}$ that depends on $a$ is now
in the context containing $\cC\{a : \bW \sigma; ..\}$.
But if we want $t_{new}$ to be inherited(reused) when $\sigma$ is
extended, we would like $t_{new}$ to be in the context containing
$\cC\{a : \cU; ..\}$ instead. The sealing is responsible for this
because we have a sealing $\goodTerm{\Gamma, \cC\{a : \bW \sigma;
..\}}{s}{\cC\{a : \cU; ..\}}$ = $\goodTerm{\Gamma, (\Sigma a : \bW
\sigma,..)}{s}{(\Sigma a : \cU,..)}$. Then we can construct
$t_{new}$ in the context containing $(\Sigma a : \cU,..)$, ready for
inheritance.
Apparently $t_{new}$ in this case cannot be doing \textit{exhaustiveness
checking}, but it can freely use any \textit{exhaustiveness-checked}
recursor.
%\YZ{It occurs to me that you use the word "sealing" to mean
%different (though tangentially related) things. Previously you used it
%as in "sealed families".}\EDJreply{They are actually the same thing.
%This sealing in metatheory is much stronger than that of the implemented
%plugin. Downside of the strong sealing is that if the user really use
%this version of sealing, the user will have to annotate what the sealed
%family type is. Now in the plugin, the sealed family type is almost
%fixed (directly inferred using a fixed rules). So basically this
%complete version of sealing (in metatheory) can deduce that of seal (in
%plugin implementation)}
